{\plant}: A package for modelling forest trait ecology \& evolution

### 2015-09-01 ms.tex
Update release script and word count for resubmission

\title{{\plant}: A package for modelling forest trait ecology \& evolution}
\author{Daniel S. Falster\textdagger\textasteriskcentered, Richard G. FitzJohn\textdagger, and Mark Westoby}
\affiliation{
Department of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia\\
\textdagger These authors contributed equally.\\
\textasteriskcentered Email for correspondence: \texttt{daniel.falster@mq.edu.au}\\
A manuscript in consideration as an Applications Note for
publication in MEE as part of the Special Feature \emph{Demography
  beyond the Population}.\\
Word count: ~3900 words}
\date{}

@@

The {\plant} package implements an individual-based model, meaning the dynamics of the
population arise from rules specifying how individuals grow and interact.
Being driven by traits, the model can be extended to potentially very many species. The
core rules in {\plant} are about the short-term physiological
functioning of an individual plant and how this is influenced by its
traits, size and light environment.  While {\plant} includes a core physiological model, the present paper uses it only as an example, to illustrate how one can take a given physiological model and infer simulate ecological and evolutionary outcomes. Thus, we do not aim to justify the particular physiological model used, to provide detailed
comparisons to data, or to promote this physiological model over those
in other \textsc{TSPMs}. (These are all topics deserving substantially
more attention than can be afforded here.)
% TODO: I'm a bit concerned that while we know that this is possible,
% it's not that well developed and does require compiling a new
% version of plant.  So it's not that _usefully_ extendable.  On the
% other hand, the population of users who will do this is not very
% large.  It might be possible to allow runtime linkage though if I
% push a little more of the cpp code into headers and do some tweaking
% in RcppR6...
An important feature of {\plant} considered as a software package is that it allows for users to substitute their own physiological models.

>>>>

\title{{\plant}: A package for modelling forest trait ecology \& evolution}
\author{Daniel S. Falster\textdagger\textasteriskcentered, Richard G. FitzJohn\textdagger, and Mark Westoby}
\affiliation{
Department of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia\\
\textdagger These authors contributed equally.\\
\textasteriskcentered Email for correspondence: \texttt{daniel.falster@mq.edu.au}\\
A manuscript in consideration as an Applications Note for
publication in MEE as part of the Special Feature \emph{Demography
  beyond the Population}.\\
Word count: ~4200 words}
\date{}

@@

The {\plant} package implements an individual-based model, meaning the dynamics of the
population arise from rules specifying how individuals grow and interact.
Being driven by traits, the model can be extended to potentially very many species. The
core rules in {\plant} are about the short-term physiological
functioning of an individual plant and how this is influenced by its
traits, size and light environment.  While {\plant} includes a core physiological model, the present paper uses it only as an example, to illustrate how one can take a given physiological model and simulate ecological and evolutionary outcomes. Thus, we do not aim to justify the particular physiological model used, to provide detailed
comparisons to data, or to promote this physiological model over those
in other \textsc{TSPMs}. (These are all topics deserving substantially
more attention than can be afforded here.)
% TODO: I'm a bit concerned that while we know that this is possible,
% it's not that well developed and does require compiling a new
% version of plant.  So it's not that _usefully_ extendable.  On the
% other hand, the population of users who will do this is not very
% large.  It might be possible to allow runtime linkage though if I
% push a little more of the cpp code into headers and do some tweaking
% in RcppR6...
An important feature of {\plant} considered as a software package is that it allows for users to substitute their own physiological models.
